Test susieI using chr17 to 22

### 2020-10-02 analysis/simulation-susieI-ukbchr17to22-gtex.adipose.Rmd
batch susieI

  m <- cbind(df[,"pi1.gene_mr.ash2"]/df[,"pi1.SNP_mr.ash2"], 1:nrow(df), 1 + 1:nrow(df)/nrow(df)/3)
  st <-  cbind(df[,"pi1.gene_susietruth"]/df[,"pi1.SNP_susietruth"], 1:nrow(df), 2 + 1:nrow(df)/nrow(df)/3)
  s <- cbind(df[,"pi1.gene_susieI"]/df[,"pi1.SNP_susieI"], 1:nrow(df), 3 + 1:nrow(df)/nrow(df)/3)
  t <- df[1,"pi1.gene_truth"]/df[1,"pi1.SNP_truth"]
  dfp <- rbind(m,st,s)
  plot(dfp[,3], dfp[,1], col = dfp[,2], pch = 19, ylab = "Enrichment (gene/snp)", xaxt = "n", xlab="", xlim = c(0.8, 3.5),frame.plot=FALSE, ylim = c(0, min(max(dfp[,1],t) *1.05, 150)))
  axis(side=1, at=1:3, labels = FALSE, tick = F)
  text(x=1:3, 0, labels = c("mr.ash2", "susieI_truth", "susieI"), xpd = T, pos =1)
  abline(h= t, lty = 2, col= "darkgreen", lwd=1.5)
  grid()
}
```

@@

@@

@@

@@

@@

## Regions: TWAS gene+SNP

@@

@@

@@

@@

## Regions: TWAS BF

* Regions: regional TWAS BF > 2

>>>>

  m <- cbind(df[,"pi1.gene_mr.ash2"]/df[,"pi1.SNP_mr.ash2"], 1:nrow(df), 1 + 1:nrow(df)/nrow(df)/3)
  st <-  cbind(df[,"pi1.gene_susietruth"]/df[,"pi1.SNP_susietruth"], 1:nrow(df), 2 + 1:nrow(df)/nrow(df)/3)
  s <- cbind(df[,"pi1.gene_susieI"]/df[,"pi1.SNP_susieI"], 1:nrow(df), 3 + 1:nrow(df)/nrow(df)/3)
  t <- df[1,"pi1.gene_truth"]/df[1,"pi1.SNP_truth"]
  dfp <- rbind(m,st,s)
  plot(dfp[,3], dfp[,1], col = dfp[,2], pch = 19, ylab = "Enrichment (gene/snp)", xaxt = "n", xlab="", xlim = c(0.8, 3.5),frame.plot=FALSE, ylim = c(0, min(max(dfp[,1],t) *1.05, 150)))
  axis(side=1, at=1:3, labels = FALSE, tick = F)
  text(x=1:3, 0, labels = c("mr.ash2", "susieI_truth", "susieI"), xpd = T, pos =1)
  abline(h= t, lty = 2, col= "darkgreen", lwd=1.5)
  grid()
}

gpip_dist <- function(susiefs, ...){
  dflist <- list()
  for (f in susiefs){
    dflist[[f]] <- read.table(f, header =T , stringsAsFactors = F)
  }
  df <- do.call(rbind, dflist)
  hist(df[df$type == "gene", "susie_pip"], xlab = "gene susie PIP", 
       breaks = 50, ylim = c(0,20), xlim=c(0,1), col = "salmon", ...)
}
```

@@

```{r pipdist,fig.height=3, fig.width=9}
par(mfrow = c(1,3))
gpip_dist(susieIfs2[1:5], main = "1-x combined")
gpip_dist(susieIfs2[6:10], main = "2-x combined")
gpip_dist(susieIfs2[11:15], main = "3-x combined")
```

@@

df <- show_param(mrashfs, susieIfs, susieIfs2)
par(mfrow = c(4,2))
plot_param(df[1:5,], main = "1-x: gene.pve ~ 0.01, snp.pve ~ 0.05")
plot_param(df[6:10,], main = "2-x: gene.pve ~ 0.01, snp.pve ~ 0.05")
plot_param(df[11:15,], main = "3-x: gene.pve ~ 0.01, snp.pve ~ 0.05")
plot_param(df[16:20,], main = "4-x: gene.pve ~ 0.05, snp.pve ~ 0.05")
```
```{r pipdist-6,fig.height=3, fig.width=12}
par(mfrow = c(1,4))
gpip_dist(susieIfs2[1:5], main = "1-x combined")
gpip_dist(susieIfs2[6:10], main = "2-x combined")
gpip_dist(susieIfs2[11:15], main = "3-x combined")
gpip_dist(susieIfs2[16:20], main = "4-x combined")
```

@@

```{r pipdist-7,fig.height=3, fig.width=12}
par(mfrow = c(1,4))
gpip_dist(susieIfs2[1:5], main = "1-x combined")
gpip_dist(susieIfs2[6:10], main = "2-x combined")
gpip_dist(susieIfs2[11:15], main = "3-x combined")
gpip_dist(susieIfs2[16:20], main = "4-x combined")
```

@@

df <- show_param(mrashfs, susieIfs, susieIfs2)
par(mfrow = c(4,2))
plot_param(df[1:5,], main = "1-x: gene.pve ~ 0.01, snp.pve ~ 0.05")
plot_param(df[6:10,], main = "2-x: gene.pve ~ 0.01, snp.pve ~ 0.05")
plot_param(df[11:15,], main = "3-x: gene.pve ~ 0.01, snp.pve ~ 0.05")
plot_param(df[16:20,], main = "4-x: gene.pve ~ 0.05, snp.pve ~ 0.05")
```
```{r pipdist-9,fig.height=3, fig.width=12}
par(mfrow = c(1,4))
gpip_dist(susieIfs2[1:5], main = "1-x combined")
gpip_dist(susieIfs2[6:10], main = "2-x combined")
gpip_dist(susieIfs2[11:15], main = "3-x combined")
gpip_dist(susieIfs2[16:20], main = "4-x combined")
```

@@

df <- show_param(mrashfs, susieIfs, susieIfs2)
par(mfrow = c(4,2))
plot_param(df[1:5,], main = "1-x: gene.pve ~ 0.01, snp.pve ~ 0.05")
plot_param(df[6:10,], main = "2-x: gene.pve ~ 0.01, snp.pve ~ 0.05")
plot_param(df[11:15,], main = "3-x: gene.pve ~ 0.01, snp.pve ~ 0.05")
plot_param(df[16:20,], main = "4-x: gene.pve ~ 0.05, snp.pve ~ 0.05")
```
```{r pipdist-10,fig.height=3, fig.width=12}
par(mfrow = c(1,4))
gpip_dist(susieIfs2[1:5], main = "1-x combined")
gpip_dist(susieIfs2[6:10], main = "2-x combined")
gpip_dist(susieIfs2[11:15], main = "3-x combined")
gpip_dist(susieIfs2[16:20], main = "4-x combined")
```

## Regions: TWAS gene+SNP top

@@

df <- show_param(mrashfs, susieIfs, susieIfs2)
par(mfrow = c(4,2))
plot_param(df[1:5,], main = "1-x: gene.pve ~ 0.01, snp.pve ~ 0.05")
plot_param(df[6:10,], main = "2-x: gene.pve ~ 0.01, snp.pve ~ 0.05")
plot_param(df[11:15,], main = "3-x: gene.pve ~ 0.01, snp.pve ~ 0.05")
plot_param(df[16:20,], main = "4-x: gene.pve ~ 0.05, snp.pve ~ 0.05")
```
```{r pipdist-11,fig.height=3, fig.width=12}
par(mfrow = c(1,4))
gpip_dist(susieIfs2[1:5], main = "1-x combined")
gpip_dist(susieIfs2[6:10], main = "2-x combined")
gpip_dist(susieIfs2[11:15], main = "3-x combined")
gpip_dist(susieIfs2[16:20], main = "4-x combined")
```

## Regions: TWAS gene+SNP BF

* Regions: get BF for both genes and SNPs. regional TWAS BF > 2

df <- show_param(mrashfs, susieIfs, susieIfs2)
par(mfrow = c(4,2))
plot_param(df[1:5,], main = "1-x: gene.pve ~ 0.01, snp.pve ~ 0.05")
plot_param(df[6:10,], main = "2-x: gene.pve ~ 0.01, snp.pve ~ 0.05")
plot_param(df[11:15,], main = "3-x: gene.pve ~ 0.01, snp.pve ~ 0.05")
plot_param(df[16:20,], main = "4-x: gene.pve ~ 0.05, snp.pve ~ 0.05")
```
```{r pipdist-5,fig.height=3, fig.width=12}
par(mfrow = c(1,4))
gpip_dist(susieIfs2[1:5], main = "1-x combined")
gpip_dist(susieIfs2[6:10], main = "2-x combined")
gpip_dist(susieIfs2[11:15], main = "3-x combined")
gpip_dist(susieIfs2[16:20], main = "4-x combined")
```

## Regions: TWAS gene+SNP FDR

* Regions: put gene and SNP pvalues together and get FDR. Seelect regions with minimum FDR < 0.05.

```{r param 13, fig.height=11, fig.width=6}
tags <- paste(rep(1:4, each = 5), 1:5, sep = "-")
mr.ashfs <- paste0(mrashdir, "20200721-", tags, "-mr.ash2s.lassoes-es.param.txt")
susieIfs <- paste0(outputdir, "20200813-", tags, ".config13.susieIres.Rd")
susieIfs2 <- paste0(outputdir, "20200813-", tags, ".config13.susieI.txt")

df <- show_param(mrashfs, susieIfs, susieIfs2)
par(mfrow = c(4,2))
plot_param(df[1:5,], main = "1-x: gene.pve ~ 0.01, snp.pve ~ 0.05")
plot_param(df[6:10,], main = "2-x: gene.pve ~ 0.01, snp.pve ~ 0.05")
plot_param(df[11:15,], main = "3-x: gene.pve ~ 0.01, snp.pve ~ 0.05")
plot_param(df[16:20,], main = "4-x: gene.pve ~ 0.05, snp.pve ~ 0.05")
```
```{r pipdist-13,fig.height=3, fig.width=12}
par(mfrow = c(1,4))
gpip_dist(susieIfs2[1:5], main = "1-x combined")
gpip_dist(susieIfs2[6:10], main = "2-x combined")
gpip_dist(susieIfs2[11:15], main = "3-x combined")
gpip_dist(susieIfs2[16:20], main = "4-x combined")
```

@@

df <- show_param(mrashfs, susieIfs, susieIfs2)
par(mfrow = c(4,2))
plot_param(df[1:5,], main = "1-x: gene.pve ~ 0.01, snp.pve ~ 0.05")
plot_param(df[6:10,], main = "2-x: gene.pve ~ 0.01, snp.pve ~ 0.05")
plot_param(df[11:15,], main = "3-x: gene.pve ~ 0.01, snp.pve ~ 0.05")
plot_param(df[16:20,], main = "4-x: gene.pve ~ 0.05, snp.pve ~ 0.05")
```
```{r pipdist-3,fig.height=3, fig.width=12}
par(mfrow = c(1,4))
gpip_dist(susieIfs2[1:5], main = "1-x combined")
gpip_dist(susieIfs2[6:10], main = "2-x combined")
gpip_dist(susieIfs2[11:15], main = "3-x combined")
gpip_dist(susieIfs2[16:20], main = "4-x combined")
```

@@

df <- show_param(mrashfs, susieIfs, susieIfs2)
par(mfrow = c(4,2))
plot_param(df[1:5,], main = "1-x: gene.pve ~ 0.01, snp.pve ~ 0.05")
plot_param(df[6:10,], main = "2-x: gene.pve ~ 0.01, snp.pve ~ 0.05")
plot_param(df[11:15,], main = "3-x: gene.pve ~ 0.01, snp.pve ~ 0.05")
plot_param(df[16:20,], main = "4-x: gene.pve ~ 0.05, snp.pve ~ 0.05")
```
```{r pipdist-4,fig.height=3, fig.width=12}
par(mfrow = c(1,4))
gpip_dist(susieIfs2[1:5], main = "1-x combined")
gpip_dist(susieIfs2[6:10], main = "2-x combined")
gpip_dist(susieIfs2[11:15], main = "3-x combined")
gpip_dist(susieIfs2[16:20], main = "4-x combined")
```

@@
